\section*{Acknowledgments}

We are very grateful to the authors of Ref.~\cite{Chatterjee:2019avs} for fruitful discussions and for sharing their work that helped us to directly compare our methods to those used in
\ac{LVK}'s \ac{O3} observing run. We would also like to thank \tocheck{Tito Dal Canton and Thomas Dent for their useful comments} and the many other colleagues of the LIGO Scientific Collaboration and the Virgo Collaboration who have provided invaluable help over
the years.

This work is based upon work supported by the LIGO Laboratory which is a major facility fully funded by the National Science Foundation. We are grateful for computational resources provided by
the LIGO Laboratory and supported by the U.S.\ National Science Foundation Awards PHY-0757058 and PHY-0823459. 

M.B.\ is partiallly supported by the Spanish Agencia Estatal de Investigaci\'on grant PID2020-118236GB-I00. M.M.T.\ is partially supported by the Ministerio de Universidades de Espa\~na (Spanish
Ministry of Universities) through the ``Ayuda para la Formaci\'on de Profesorado Universitario'' (FPU) grant FPU19/01750, by the Spanish Agencia Estatal de Investigaci\'on grants
PGC2018-095984-B-I00 and PID2021-125485NB-C21 funded by MCIN/AEI/10.13039/501100011033 and the European Regional Development Fund (ERDF) ``A way of making Europe,'' and by the Generalitat
Valenciana (Prometeo grant CIPROM/2022/49). S.S.C.\ and Y.Z.\ are partially supported by the U.S.\ National Science Foundation under awards PHY-2011334 and PHY-2308693. M.C.\ is partially
supported by the U.S.\ National Science Foundation under awards PHY-2011334, PHY-2219212 and PHY-2308693. L.M.Z.\ is partially supported by the MSSGC Graduate Research Fellowship, awarded
through the NASA Cooperative Agreement 80NSSC20M0101. D.T.~is partially supported by the Spanish Agencia Estatal de Investigaci\'on grant PID2021-125485NB-C21 funded by
MCIN/AEI/10.13039/501100011033 and ERDF ``A way of making Europe,'' and by the Generalitat Valenciana (Prometeo grant CIPROM/2022/49).

\tocheck{M.W.C.\ acknowledges support from the National Science Foundation with grant numbers PHY-2308862 and OAC-2117997. A.T.\ acknowledges support from the National Science Foundation with grant numbers PHY-2010970 and OAC-2117997.}

\tocheck{\sout{Part of this research was performed} This research was initiated by M.B, M.M.T., S.A., M.C., L.M.Z., D.T., and Y.Z.\ during their stay} at the Institute of Pure and
Applied Mathematics (IPAM),  University of California Los-Angeles (UCLA). IPAM is partially supported by the National Science Foundation through award DMS-1925919. These authors
would like to thank IPAM and UCLA for their warm hospitality.

Software for this analysis is written in \texttt{Python} 3.x~\cite{python3} and uses standard Open Source libraries and community-contributed modules from the Python Package Index
(PyPI) repository~\cite{pypi} including \texttt{numpy}~\cite{harris2020array}, \texttt{scipy}~\cite{2020SciPy-NMeth},
\texttt{pandas}~\cite{reback2020pandas,mckinney-proc-scipy-2010}, \texttt{matplotlib}~\cite{Hunter:2007ouj}, and \texttt{sklearn}~\cite{scikit-learn}.

This manuscript has been assigned LIGO Document Control Center number P2300338.

\tocheck{\textbf{Author contribution statement.} M.B.\ and M.M.T.\ designed the \ac{RF} and \ac{KNN} models and their computational framework, respectively, and ran the corresponding analyses.
S.S.C.\ curated the data sets and contributed to the analysis, particularly the comparison with the current \ac{LVK} \ac{KNN} implementation. M.C.\ directed the project. S.A., L.M.Z., D.T., and
Y.Z.\ contributed to all aspects of this work, including but not limited to the design and implementation of the research, data analysis, and manuscript writing.  Authorship for the \ac{LVK}
members of the \ac{MDC} builder's list is requested in publications resulting from the \ac{MDC} data set.  M.W.C., S.G., and A.T.\ are opt-in members of this list. M.W.C.\ and S.G. also provided
useful comments during the internal \ac{LVK} review period. The authors gratefully thank the other opt-out members of the \ac{MDC} builder's list for creating the set, and/or providing summary
statistics based on its results, and making these products available to the \ac{LVK} collaborations: Sarah Antier, Patrick J.~Brockill,  Deep Chatterjee, Reed Essick, Patrick Godwin, Erik
Katsavounidis, and Gaurav Waratkar.}






